The College Application Problem

### 2022-05-08 slides_08min/slides.tex
refs

\ifen 
\title{The College Application Problem}
\author{Max Kapur}
\institute{Seoul National University\\
Department of Industrial Engineering \\
Management Science/Optimization Lab\\
\url{maxkapur@snu.ac.kr}}
\date{\today}
\else
\title[대학 지원 최적화 문제]{대학 지원 최적화 문제}
\author{Max Kapur}
\institute{서울대학교 산업공학과 \\
경영과학/최적화 연구실\\
\url{maxkapur@snu.ac.kr}}
\date{\today}
\fi

@@

 \setbeamertemplate{caption}[numbered]
\setbeamertemplate{footline} {
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.27\paperwidth,ht=2.65ex,dp=1.2ex,left]{date in head/foot}%
  \hspace*{1ex}
    \ifnum \theframenumber=1{}
    \else \insertshorttitle%~\textbar~\insertsectionhead
    \fi
     \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.23\paperwidth,ht=2.65ex,dp=1.2ex,right]{date in head/foot}%
    \ifnum \theframenumber=1{}
    \else \insertsectionhead
    \fi
  \hspace*{2ex}
     \end{beamercolorbox}%
       \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertdate
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.65ex,dp=1.2ex,right]{author in head/foot}%
    \insertframenumber{} / \inserttotalframenumber
    \hspace*{1.5ex}
  \end{beamercolorbox}
}%
  \vskip0pt%
}

@@

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, FPTAS memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{결론}
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제는 \textbf{이론적인 흥미가 깊다}. Submodular 최대화 문제지만, 근사 해법의 성질은 배낭 문제에 더 가깝다.

@@

%Fisher, Marshall, George Nemhauser, and Laurence Wolsey. 1978. ``An analysis of approximations for maximizing submodular set functions—I.'' \emph{Mathematical Programming} 14: 265--94.

>>>>

\ifen 
\title{The College Application Problem}
\author{Max Kapur}
\institute{Seoul National University\\
Department of Industrial Engineering \\
Management Science/Optimization Lab\\
\url{maxkapur@snu.ac.kr}\\}
\date{May 13, 2022}
\else
\title[대학 지원 최적화 문제]{대학 지원 최적화 문제}
\author{Max Kapur}
\institute{서울대학교 산업공학과 \\
경영과학/최적화 연구실\\
\url{maxkapur@snu.ac.kr}\\
\vspace{0.5em}
지도 교수: 홍성필}
\date[2022년 5월 13일]{2022년 5월 13일\\석사논문합동발표회}
\fi

@@

 \setbeamertemplate{caption}[numbered]
\setbeamertemplate{footline} {
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.27\paperwidth,ht=2.65ex,dp=1.2ex,left]{date in head/foot}%
  \hspace*{1ex}
    \ifnum \theframenumber=1{}
    \else \insertshorttitle%~\textbar~\insertsectionhead
    \fi
     \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.23\paperwidth,ht=2.65ex,dp=1.2ex,right]{date in head/foot}%
    \ifnum \theframenumber=1{}
    \else \insertsectionhead
    \fi
  \hspace*{2ex}
     \end{beamercolorbox}%
       \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertshortdate
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.65ex,dp=1.2ex,right]{author in head/foot}%
    \insertframenumber{} / \inserttotalframenumber
    \hspace*{1.5ex}
  \end{beamercolorbox}
}%
  \vskip0pt%
}

@@

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack (cf. Fisher et al. 1978, Kulik et al. 2013).

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, FPTAS memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{결론}
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제는 \textbf{이론적인 흥미가 깊다}. Submodular 최대화 문제지만, 근사 해법의 성질은 배낭 문제에 더 가깝다 (cf. Fisher et al. 1978, Kulik et al. 2013).

@@

Fisher, Marshall, George Nemhauser, and Laurence Wolsey. 1978. ``An analysis of approximations for maximizing submodular set functions—I.'' \emph{Mathematical Programming} 14: 265--94.

### 2022-05-08 slides_20min/slides.tex
confirm title slide to conference guidelines
refs

\ifen 
\title{The College Application Problem}
\author{Max Kapur and Sung-Pil Hong}
\institute{Seoul National University\\
Department of Industrial Engineering \\
Management Science/Optimization Lab\\
\url{maxkapur@snu.ac.kr}}
\date{\today\\
Spring Conference of the Korean Institute of Industrial Engineers}
\else
\title[대학 지원 최적화 문제]{대학 지원 최적화 문제\\The College Application Problem}
\author{Max Kapur, 홍성필}
\institute{서울대학교 산업공학과\\
경영과학/최적화 연구실\\
\url{maxkapur@snu.ac.kr}}
\date{\today\\
대한산업공학회 춘계공동학술대회}
\fi

@@

 \setbeamertemplate{caption}[numbered]
\setbeamertemplate{footline} {
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.27\paperwidth,ht=2.65ex,dp=1.2ex,left]{date in head/foot}%
  \hspace*{1ex}
    \ifnum \theframenumber=1{}
    \else \insertshorttitle%~\textbar~\insertsectionhead
    \fi
     \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.23\paperwidth,ht=2.65ex,dp=1.2ex,right]{date in head/foot}%
    \ifnum \theframenumber=1{}
    \else \insertsectionhead
    \fi
  \hspace*{2ex}
     \end{beamercolorbox}%
       \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}%\insertdate
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.65ex,dp=1.2ex,right]{author in head/foot}%
    \insertframenumber{} / \inserttotalframenumber
    \hspace*{1.5ex}
  \end{beamercolorbox}
}%
  \vskip0pt%
}

@@

>>>>

\ifen 
\title{The College Application Problem}
\author{Max Kapur and Sung-Pil Hong}
\institute{Seoul National University\\
Department of Industrial Engineering\\
Management Science/Optimization Lab\\
\url{maxkapur@snu.ac.kr}}
\date[\today]{\today\\
Spring Conference of the Korean Institute of Industrial Engineers}
\else
\title[대학 지원 최적화 문제]{대학 지원 최적화 문제\\The College Application Problem}
\author[Max Kapur, 홍성필 교수]{Max Kapur, \underline{홍성필 교수}}
\institute{서울대학교 산업공학과\\
경영과학/최적화 연구실\\
\{maxkapur, \underline{sphong}\}@snu.ac.kr}
\date[\today]{\today\\
대한산업공학회 춘계공동학술대회}
\fi

@@

 \setbeamertemplate{caption}[numbered]
\setbeamertemplate{footline} {
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.25\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.27\paperwidth,ht=2.65ex,dp=1.2ex,left]{date in head/foot}%
  \hspace*{1ex}
    \ifnum \theframenumber=1{}
    \else \insertshorttitle%~\textbar~\insertsectionhead
    \fi
     \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.23\paperwidth,ht=2.65ex,dp=1.2ex,right]{date in head/foot}%
    \ifnum \theframenumber=1{}
    \else \insertsectionhead
    \fi
  \hspace*{2ex}
     \end{beamercolorbox}%
       \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.65ex,dp=1.2ex,left]{author in head/foot}%
  \hspace*{1.5ex}\insertshortdate
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.65ex,dp=1.2ex,right]{author in head/foot}%
    \insertframenumber{} / \inserttotalframenumber
    \hspace*{1.5ex}
  \end{beamercolorbox}
}%
  \vskip0pt%
}

@@

￣
